data-explore

### 2019-01-07 bda/analysis/BDA-analysis.Rmd
update directory structure. add paper outline.

Note: this analysis includes 85% of participants as I'm having trouble modeling what appears to be fairly random behaviors... See `analysis.ipynb` for more information.
```{r getModelableData}
# Hueristic modelable data
f_modelable_data <- "../modelable-data-20180330.csv"
dfModelable <- read.csv(f_modelable_data)

# All data
f_all_data <- "../kanwal-preprocessed.csv"
dfAll <- read.csv(f_all_data) %>%
  mutate(frequent=round(frequent, 2),
         infrequent=round(infrequent, 2))
```

```{r setup-bda-model}
f_bda_model <- "../kanwal-BDA-20180330.wppl"
model_bda <- getModelFile(f_bda_model)
bda_data <- head(dfModelable)
nrow(dfModelable)

problemIPs <- c('70.198.5.150', 
                '117.217.210.9', 
                '65.183.140.246', 
                '24.253.233.194', 
                '24.20.229.200', 
                '108.196.136.202',
                '122.161.26.31')
# 24.74.13.244 only after 10000 attempts
# 50.153.162.232
# 
# but worked on second time
dfAll2 <- dfAll %>% filter(!(IP %in% problemIPs))
```

Note: slow running.
```{r run-bda-model}
# pt <- proc.time()
# df_bda <- rwebppl::webppl(model_bda, data=dfAll2, data_var='rData')
# et <- proc.time() - pt
# write.csv(df_bda, "bda-tuned-params-20180303.csv")
```

>>>>

Note: this analysis includes 85% of participants as I'm having trouble modeling what appears to be fairly random behaviors... See `analysis.ipynb` for more information.
```{r getModelableData}
# Hueristic modelable data
f_modelable_data <- "../data/modelable-data-20180330.csv"
dfModelable <- read.csv(f_modelable_data)

# All data
f_all_data <- "../data/kanwal-preprocessed.csv"
dfAll <- read.csv(f_all_data) %>%
  mutate(frequent=round(frequent, 2),
         infrequent=round(infrequent, 2))
```

```{r setup-bda-model}
f_bda_model <- "../models/kanwal-BDA-20180330.wppl"
model_bda <- getModelFile(f_bda_model)
bda_data <- head(dfModelable)
nrow(dfModelable)

problemIPs <- c('70.198.5.150', 
                '117.217.210.9',   # this ones the killer
                '65.183.140.246', 
                '24.253.233.194', 
                '24.20.229.200', 
                '108.196.136.202',  # this ones not bad
                '122.161.26.31')
# 24.74.13.244 only after 10000 attempts
# 50.153.162.232
# 
# but worked on second time
# dfAll2 <- dfAll %>% filter(!(IP %in% problemIPs))
dfAll2 <- dfAll %>% filter(IP %in% problemIPs)
```

Note: slow running.
```{r run-bda-model}
pt <- proc.time()
df_bda <- rwebppl::webppl(model_bda, data=dfAll2, data_var='rData')
et <- proc.time() - pt
# write.csv(df_bda, "bda-tuned-params-20180303.csv")
```

### 2019-01-07 bda/analysis/data-explore.Rmd
update directory structure. add paper outline.

```{r libs}
library(ggthemes)
library(tidyverse)
```

@@

```{r data}
df <- read.csv("../data/df_agg.csv")
```

>>>>

```{r libs}
rm(list=ls())
library(ggthemes)
library(jsonlite)
library(tidyverse)
```

@@

# Reproduce Fig 5.

```{r}
f_all_data <- "../data/df_agg.csv"
dfAll <- read.csv(f_all_data)
```

```{r}
dfAll %>%
  filter(condition=='combined') %>%
  select(IP, condition, label, conditional_trial_num, label_type, display_type) %>%
  group_by(conditional_trial_num, display_type)

```

```{r}
dfAll %>%
  filter(condition=='combined') %>%
  select(IP, condition, label, conditional_trial_num, label_type, display_type) %>%
  mutate(wordLength=nchar(label)) %>%
  group_by(conditional_trial_num, display_type) %>%
  summarise(n=n(),
            avgLen=mean(wordLength),
            ci_high=avgLen+1.96*sd(wordLength)/sqrt(n),
            ci_low=avgLen-1.96*sd(wordLength)/sqrt(n)) %>%
  ggplot(aes(x=conditional_trial_num, y=avgLen, col=display_type)) +
    geom_point() +
    geom_line() +
    geom_errorbar(aes(ymax=ci_high, ymin=ci_low), col='grey', alpha=0.7, width=0.5) +
    ylim(3, 7) +
    theme_few() +
    ggtitle("Reproducing Fig 5.")
```

```{r}
dfPropData <- dfAll %>%
  filter(condition=='combined') %>%
  select(IP, condition, label, conditional_trial_num, label_type, display_type) %>%
  mutate(isShortLabel=label_type=='short') %>%
  group_by(conditional_trial_num, display_type) %>%
  summarise(n=n(),
            propShort=mean(isShortLabel),
            ci_high=propShort+1.96*sqrt(propShort*(1-propShort)/n),
            ci_low=propShort-1.96*sqrt(propShort*(1-propShort)/n))

dfPropData %>%
  ggplot(aes(x=conditional_trial_num, y=propShort, col=display_type)) +
    geom_errorbar(aes(ymax=ci_high, ymin=ci_low)) +
    geom_line() +
    ylim(0, 1) +
    theme_few() +
    ggtitle("Proportion of times using the short form over repetition.")

# write.csv(dfPropData, "../data/temporalDynamicsData.csv")
```

```{r data}
df <- read.csv("../data/d _agg.csv")
```
